### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Whoops, not preventing negative harvest values can lead to some weird results.

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0) dunif(P, mu * (1 - s), mu * (1 + s))
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.integer(P == mu)
  }
}
pdfn <- Vectorize(FUN)
```

>>>>

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0){
      dlnorm(P, mu, s)
      #dunif(P, mu * (1 - s), mu * (1 + s))
    }
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.integer(P == mu)
  }
}
pdfn <- Vectorize(FUN)
```
